---
title: "Probability: Binomial Distribution"
output: html_notebook
---

## Binomial distribution in R

We are going to use a simple example: a flip coin
Assume a fair coin (50 percent of being 1 or 0), which 1 means face or success; and 0, means tail or fail.

- *n*: number of draws of a single outcome variable
- *size*: number of coins that we are going to draw or flip
- *prob*: probabilit of being 1 (face or success)

Here an example:

- *n* : 1 (1 randon flip or draw)
- *size* : 1
- *prob*: 0.5

```{r}
rbinom(n = 1,size = 1,prob = 0.8)
```

## New cases

### Case 1

We flip once **(n=1)** 10 coins (**size = 10**) with a probability of 0.8 (**prob=0.8**). In R, we write:

```{r}
rbinom(n =1, size= 10, prob=0.8)
```


- The results, let say **9** (may chage in each run code) , means that the outcome of flipping **10** coins at once **(n=1)**, we obtain **9** faces with a probabilit of 0.8


- El resultado, digamos 9 (puede variar en cada corrida), significa que al lanzar 10 monedas a la vez  (al mismo tiempo o **n=1**) podemos obtener 9 caras en total con una probabilidad de **prob=0.8**. 

- De forma generica  podemos decir que podemos obtener 9 caras al lanzar 10 monedas a la vez con una probabilidad de obtener cara en cada moneda igual a **0.8**

The beforementioned example coud be rewritten as:

```{r}
rbinom(n =10, size= 1, prob=0.8)
```

Aqui observamos que al lanzar 10 una sola moneda (size =1), obtenemos, por ejemplo **[1] 1 1 1 0 1 1 1 1 1**. Contando cada cara o exito de cada lanzamiento, contamos que 9 veces obtuvimos cara o exito en cada lanzamiento o evento.

#TODO: PONER ESTE ULTIMO EJEMPLO COMO EL PRIMERO


